A_pilot_1

### 2019-04-15 experiment_data_and_analyses/A_pilot_1.Rmd
pilot 1 formatting and plotting and tables

---
title: "A_pilot_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
    theme: default
    css: styles.css
---

@@

```{r, "lmer 1 compare different rt metrics using the same model structure", warning=FALSE}
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.rcp <- lmer(data=dat, rt_reciprocal ~ vag + subit + quan + gap + side + (1|subject) + (1|item))
```

```{r}
models <- 
rbind(
  cbind(tidy(lmer1.ms),model="ms"), 
  cbind(tidy(lmer1.log),model="log"), 
  cbind(tidy(lmer1.rcp),model="rcp")
)

dwplot(models, vline = geom_vline(xintercept = 0)) + facet_wrap(~model, scales="free", ncol=1)
```

```{r lmer on logrt, warning=FALSE}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
```

```{r, fig.width=6, fig.height=2}
dwplot(lmer2.log %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") +
  ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```

```{r}
lmer2.rcp <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item))
```

```{r}
# lmer3 is closer to the original anova than lmer2
lmer3 <- lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item))
```

```{r, fig.width=6, fig.height=2}
dwplot(lmer3 %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") + 
  ggtitle("rt_reciprocal ~ vag * subit + quan + gap + (vag+subit|subject) + (vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```

>>>>

---
title: "A_pilot_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
    theme: default
    code_folding: show
---

<style>
.main-container{width: 1500px;max-width:2800px;}
body{font-size: 13pt;}
.r{font-size: 12px;}
pre{font-size: 12px}
</style>

@@

```{r, "lmer 1 compare different rt metrics using the same model structure", warning=FALSE}
# no interaction
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
# with interaction
lmer2.ms <- lmer(data=dat, rt_ms ~          vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
lmer2.log <- lmer(data=dat, rt_log ~        vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
```

```{r}
models <- 
  rbind(
    cbind(tidy(lmer1.ms), model="ms no interaction"), 
    cbind(tidy(lmer1.log), model="log no interaction"),
    cbind(tidy(lmer2.ms), model="ms with interaction"), 
    cbind(tidy(lmer2.log), model="log with interaction")
  ) %>%
  filter(effect == 'fixed', term != "(Intercept)") %>%
  select(-group)
```

```{r, fig.height=12}
dwplot(models, vline = geom_vline(xintercept = 0)) + facet_wrap(vars(model), scales="free", ncol=1, drop=TRUE)
```

```{r}
summary(lmer2.log)$coefficients %>% kable() %>% kable_styling(full_width = FALSE, position='left')
```

<!-- Lmer2 includes the interaction of vagueness and subitizability. -->

<!-- ```{r lmer on logrt, warning=FALSE} -->
<!-- lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)) -->
<!-- ``` -->

<!-- ```{r, fig.width=6, fig.height=2} -->
<!-- dwplot(lmer2.log %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) + -->
<!--   xlab("Coefficient") + -->
<!--   ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)") +  -->
<!--   theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- lmer2.rcp <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # lmer3 is closer to the original anova than lmer2 -->
<!-- lmer3 <- lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item)) -->
<!-- ``` -->

<!-- ```{r, fig.width=6, fig.height=2} -->
<!-- dwplot(lmer3 %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) + -->
<!--   xlab("Coefficient") +  -->
<!--   ggtitle("rt_reciprocal ~ vag * subit + quan + gap + (vag+subit|subject) + (vag|item)") +  -->
<!--   theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8)) -->
<!-- ``` -->
